% subsection for Map Component

\subsection{Routing}
\begin{numerate}[NF]
\item Performance: Compute the shortest route in less than one second.
\item Performance: \textit{GUI} reacts to the user-input in less than one second.
\item Reliability: When entering an existing destination, the correct destination is found every time.
\item Flexibility: Using the Java-technology ensures the runnability of the product on all common operating systems.
\item Flexibility: The user interface is exchangeable. This means that the \textit{GUI} can be altered without changing the internal implementation of the functionalities.
\item Usability: A high user-friendliness is achieved through a simple and intuitive \textit{GUI}.
\item Usability: All menus have a consistent format.
\item Maintainability: Maintenance and expansion of the software is possible without high cost.
\item Stability: Arbitrary keypresses does not lead to a system crash or unintended behavior.
\item Stability: There can be no unhandled exceptions from incorrect user input.
\end{numerate}

\subsection{Administration tool}
\begin{numerate}[NF]
\item Flexibility: Different file formats can be loaded to use as \textit{background image}.
\item Flexibility: The user interface is exchangeable. This means that the \textit{GUI} can be altered without changing the internal implementation of the functionalities.
\item Reliability: A software crash does not cause any loss of saved data.
\item Maintainability: Maintenance and expansion of the software is possible without high cost.
%\item Usability: 90 \% of novice users can learn to operate major use cases without outside assistance.
\item Usability: The product uses symbols and words that are intuitively understandable by the target audience.
\end{numerate}
